### 2011-06-04 docs/SDC/sdc.tex
write out the form of A and note that we don't update U
fix typo
add a note about present implementation

In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in Maestro and passed into the network solver
during the reaction step.

@@

>>>>

In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in Maestro and passed into the network solver
during the reaction step.  These terms approximate the following:
\begin{eqnarray}
A_{\rho X_k} &=&  \left [- \nabla \cdot (\rho X_k \Ub) \right ]^{n+1/2} \\
A_{\rho h}   &=&  \left [- \nabla \cdot (\rho h U) + \frac{Dp_0}{Dt} \right ]^{n+1/2}
\end{eqnarray}

@@

Note also that the SDC integration by {\tt VODE} does not operate on 
the velocities at all.  That update is handled in the same fashion 
as the Strang-split version of the code.

The {\tt ignition\_simple\_SDC} burner shows how to setup the system
for {\tt use\_tfromp = T} or {\tt F}.  Presently, this implementation
does not support {\tt evolve\_base\_state = T} (in particular, we 
need to evolve $p_0$ in the RHS routine).
